Exploring probability distributions for bivariate temporal granularities

### 2019-12-09 main.Rmd
typos correct

For establishing that the fielder fielded well in a particular over, we can see how many catches and run outs were made in that particular over. If a batsman is bowled out, it does not necessarily signify good fielding. So we only include catches and run out as a measure of fielding. Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs. Let us see if this fact is true. Figure \ref{fig:field} shows the difference between run rate between two subsequent overs are negative when good fielding leads to one or two dismissals in an over, implying good fielding in one over has indeed an impact on runs scored in the subsequent overs.

@@

A dot ball is a delivery bowled without any runs scored off it. The number of dot balls is reflective of the quality of bowling in the game. Run rate of an over should ideally decrease if the number of dot balls increase. However, what is the effect of dot balls on runs scored in the subsequent over. Will players  batsman likely to go for big shots because they couldn't score good runs in the previous over? Or they should play consistently and avoid scoring high? From figure \ref{fig:exdot} shows the quantile plot of runs across overs for none, one or two dot balls per over in the facets. Each of the quantiles decrease across facets. With two dot balls per over, at least 50% of the times, run rates decrease in the subsequent over as observed through the negative values for 10th, 25th and 50th percentile quantiles.

>>>>

For establishing that the fielder fielded well in a particular over, we can see how many catches and run outs were made in that particular over. If a batsman is bowled out, it does not necessarily signify good fielding. So we only include catches and run out as a measure of fielding. Difference in runs across over should be negative if good fielding has an impact on the runs scored in the subsequent overs. Let us see if this fact is true. Figure \ref{fig:field} shows the difference between run rate between two subsequent overs are negative when good fielding leads to one dismissal in an over, implying good fielding in one over has indeed an impact on runs scored in the subsequent overs.

@@

A dot ball is a delivery bowled without any runs scored off it. The number of dot balls is reflective of the quality of bowling in the game. Run rate of an over should ideally decrease if the number of dot balls increase. However, what is the effect of dot balls on runs scored in the subsequent over. Will players  batsman likely to go for big shots because they couldn't score good runs in the previous over? Or they should play consistently and avoid scoring high? From figure \ref{fig:exdot} shows the quantile plot of runs across overs for none, one or two dot balls per over in the facets. Each of the quantiles decrease across facets. With two dot balls per over, at least 50% of the times, run rates decrease in the subsequent over as observed through the negative values for different quantiles.
